\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.qmd
Added the conclude MNIST description

The *model-in-the-data-space* helps to assess the \gD{} layout. As shown in @mnist-model-proj (a), the model provides the evidence for the non-linear structure in $10\text{-}D$. Also, by visualizing the model in $10\text{-}D$ shows some quirks. The model has a twisted pattern which actually provide evidence for the $10\text{-}D$ structure which couldn't be observed by \gD{} layout (@@mnist-model-proj (b)). Furthermore, there are some long edges which indicates the existence of the small cluster and it's so close (@@mnist-model-proj (c)).

>>>>

By visualizing the model generated for tSNE in $10\text{-}D$ helps to assess the \gD{} layout. As shown in @mnist-model-proj (a), the model provides the evidence for the non-linear structure of the digit 1 data in $10\text{-}D$. The model shows some quirks. The model's twisted pattern provides evidence for the $10\text{-}D$ data structure, which is not observed by \gD{} layout (@@mnist-model-proj (b)). Furthermore, the presence of long edges indicates the existence of the small cluster located closely together (@@mnist-model-proj (c)).

### 2024-09-06 paper.tex
Added the conclude MNIST description

The \emph{model-in-the-data-space} helps to assess the \gD{} layout. As
shown in \citet{mnist-model-proj} (a), the model provides the evidence
for the non-linear structure in \(10\text{-}D\). Also, by visualizing
the model in \(10\text{-}D\) shows some quirks. The model has a twisted
pattern which actually provide evidence for the \(10\text{-}D\)
structure which couldn't be observed by \gD{} layout
(@\citet{mnist-model-proj} (b)). Furthermore, there are some long edges
which indicates the existence of the small cluster and it's so close
(@\citet{mnist-model-proj} (c)).

>>>>

By visualizing the model generated for tSNE in \(10\text{-}D\) helps to
assess the \gD{} layout. As shown in \citet{mnist-model-proj} (a), the
model provides the evidence for the non-linear structure of the digit 1
data in \(10\text{-}D\). The model shows some quirks. The model's
twisted pattern provides evidence for the \(10\text{-}D\) data
structure, which is not observed by \gD{} layout
(@\citet{mnist-model-proj} (b)). Furthermore, the presence of long edges
indicates the existence of the small cluster located closely together
(@\citet{mnist-model-proj} (c)).
